%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{000000}
\definecolor{accentText}{HTML}{000000}
\definecolor{accentLine}{HTML}{000000}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\scshape\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\scshape\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{IGOR LISBOA}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:5521997427343}{
      \raisebox{-0.05\height} \faPhone\ +55 (21) 99742-7343} ~
    \href{mailto:igor.rodrigues.lisboa@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ igor.rodrigues.lisboa@gmail.com} ~
    \href{https://www.linkedin.com/in/igor-lisboa-261020141/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/igor-lisboa-261020141} ~
    \href{https://github.com/igor-lisboa}{
      \raisebox{-0.15\height} \faGithub\ github.com/igor-lisboa}
  }

  %---------%
  % Summary %
  %---------%

  \tinysection{Summary}
  Full stack developer with 7 years of experience in the financial, real estate, and medical industries.

  %--------%
  % Skills %
  %--------%

\section{Skills}


\begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=75pt]
  \item[\textbf{Languages}] C\#, PL/SQL, JavaScript, PHP, Java, Python, C, C++, VB, ASP.
  \item[\textbf{Technologies}] .NET, TypeScript, React, PostgreSQL, Rabbit MQ, Docker, Kubernetes, CI/CD, Azure DevOps, GIT Hub, GIT Lab, AWS, S3, SQS, Dynamo DB, Mongo DB, Redis, SQL Server, MySQL, Oracle, Vue, Laravel, Spring.
\end{itemize}



%-----------%
% Education %
%-----------%

\section{Academic Background}

\headingBf{Universidade Federal Fluminense (UFF)}{2017 - 2022} % Note: Adding year(s) exposes an implied age
\headingIt{Bachelor's degree in Information Systems}{}



%-----------%
% Languages %
%-----------%

\section{Languages}

\begin{multicols}{2}
    \headingBf{English (Advanced)}{}
    
    
    \headingBf{Portuguese (Native)}{}
\end{multicols}

  
  %------------%
  % Experience %
  %------------%

  \section{Experiences}

  \headingBf{Prognum}{Jan 2024 -- current}
  \headingIt{Software Engineer}{}
  \begin{resume_list}
    \itemTitle{Developed a module (API, Worker Services, Front-End) to automatically track the real estate asset payments.}
    \item RESULT - Approximately 90\% time savings in monitoring by analysts (resulting in approximately \textbf{BRL 200K/year} savings or around \textbf{2000 hours} saved).
    \item TECH - .NET, C\#, React, PostgreSQL, Rabbit MQ, Docker, CI/CD, GIT Hub, AWS, EDA (Event-driven architecture), TDD (Test-driven development).
  \end{resume_list}

  \headingBf{BTG Pactual Bank}{Jul 2021 -- Jan 2024}
  \headingIt{Full Stack Developer}{}
  \begin{resume_list}
    \itemTitle{Developed APIs, Worker Services, Front-Ends for trading financial assets, with flexible parameterizable rules.}
    \item RESULT - This enabled the Bank to expand its asset portfolio to include new assets with very high transaction volumes, with mandatory flexible parameterization rules. Potential AUM of more than \textbf{BRL 4 billion} per year due to the new funds in operation.
    \item TECH - .NET, C\#, React, Rabbit MQ, PostgreSQL, Docker, Kubernetes, CI/CD, Azure DevOps, Redis, AWS, S3, Dynamo, EDA (Event-driven architecture), TDD (Test-driven development).
    \vspace{5pt}
    \itemTitle{Developed scalable microservice in .NET for settling financial assets.}
    \item RESULT - Reduced the average response time from \textbf{1.2 seconds to 0.45 seconds} and centralized the daily load volume in the new microservice (previously handled by multiple disparate systems). 
    \item TECH - .NET, C\#, Vue, Rabbit MQ, PostgreSQL, Docker, Kubernetes, CI/CD, Azure DevOps, AWS, Redis, TDD (Test-driven development).
    \vspace{5pt}
    \itemTitle{Developed automation for reports for Investment Funds (Performance, Management, Portfolio Composition, Liquidity).}
    \item RESULT - Approximately 15\% time savings for 2 analysts, resulting in a savings of \textbf{BRL 150K/year}.
    \item TECH - .NET, C\#, React, Rabbit MQ, SQL Server, Docker, Kubernetes, CI/CD, Azure DevOps, AWS, TDD (Test-driven development), Razor.
  \end{resume_list}


  \headingBf{Oliveira Trust}{Oct 2020 -- Jul 2021}
  \headingIt{Software Developer}{}
  \begin{resume_list}
    \itemTitle{Developed scalable containerized APIs and queue consumers for managing investment fund operations.}
    \item RESULT - Enabled the decommissioning of modules from a legacy monolith and give a operational improvements to the analysts responsible to manage investment funds resulting in approximately  23\% time savings for analyst, resulting in a savings of BRL 67,000/year.
    \item TECH - PHP, Laravel, React, AWS, S3, SQS, SQL Server, MySQL, Docker, Kubernetes, CI/CD, GIT Lab, TDD (Test-driven development).
  \end{resume_list}


  \headingBf{Intercraft}{Nov 2016 -- Oct 2020}
  \headingIt{Full Stack Developer}{}
  \begin{resume_list}
    \itemTitle{Developed a voting module (API, Front-End) that was used in medical society elections.}
    \item RESULT - This product eliminated the need for voters to travel to the headquarters and manually tally votes by 3 employees of the medical societies. Everything is now handled via the system in an easy and direct manner.
    \item TECH - Laravel, PHP, MySQL, React, IIS.
    
    \vspace{5pt}
    \itemTitle{Developed a platform for registration, configuration, and provision of 360ยบ virtual tours.}
    \item RESULT - Once it made virtual tours available, our real estate client saw an increase in website traffic and an improvement in visitor retention.
    \item TECH - Laravel, PHP, MYSQL, Vue, IIS.
    
    \vspace{5pt}
    \itemTitle{Developed a system for issuing and processing invoices for medical societies and condominiums.}
    \item RESULT - Automation to register invoices and process payments automatically replaced what previously required a team of 6 people at just one of the clients.
    \item TECH - .NET, C\#, React, PostgreSQL, Docker, GIT Hub, Windows Forms.
  \end{resume_list}


  

\end{document}